---
title: "R Notebook"
output: html_notebook
author: "Brianna Cabrera"
date: "10/1/19"
---

```{r setup}
library(nycflights13)
library(tidyverse)
install.packages("nycflights13")
"nycflights13"
```


##5.2.4 Exercises

#1
```{r}
?flights
flights
filter(flights, arr_delay >= 2) #1
filter(flights, dest == "IAH") #2
airlines
filter(flights, (carrier == "UA" | carrier == "AA" | carrier == "DL")) #3
filter(flights, (month == 7 | month == 8 | month == 9)) #4
filter(flights, arr_delay > 2, dep_delay == 0) #5
filter(flights, dep_delay <= 1, air_time >= 30) #6
filter(flights, (dep_time >= 0000 | dep_time <= 600)) #7
```

#2
```{r}
?between()
```
It finds the values between two values. This code could have been useful for number 7.

#3
```{r}
dep<-select(flights, dep.time)
```

```{r}
is.na.data.frame(flights)
```

#4
These aren't missing because those would have to be exactly present in the data. 

##5.3.1 Exercises
#1
```{r}
arrange(flights)
arrange(flights, desc(dep_delay)) #2
arrange(flights, desc(air_time)) #3
```
#4 
Flight 15 travelled the longest while flight 167 traveled the shortest.

##5.4.1 Exercises

1. 
```{r}
select(flights, dep.time)
select(flights, dep_delay)
select(flights, arr_time)
select(flights, arr_delay)
```
#2
```{r}
select(flights, dep.time, dep_delay, arr_time, arr_delay)
```
This code only shows the values from the columns that I put in the code.

#3
```{r}
?one_of()
```

#4
```{r}
select(flights, contains("TIME"))
```
This doesn't surprise me because every column shown has "time" in the title just like we had asked for in the code.

##5.5.2 Exercises
#1. 
```{r}
transmute(flights,
       sched_arr_time - dep_time)
```
#2.
```{r}
select(flights, air_time)
transmute(flights, 
            arr_time - dep_time)
```
The calculation has larger numbers.

#3

```{r}
select(flights, dep_time, sched_dep_time, dep_delay)
```
dep_time should be the same number as sched_dep_time and dep_delay should be zero.

#4
```{r}
?min_rank
```

#5
```{r}
1:3 + 1:10
```
Results in an error because these ratios cannot be used as values to use for calculations.

#6
R provides tangent, cosine, sin, and their inverses.

##5.6.7 Exercises

#1 
You can use group_by(), summarise(), count(), sum(), and ungroup()
Departure delay is more important.

#2
```{r}

```

#3
Departure delay is more important.

#6
```{r}
?sort
```
It sorts data frames.

##5.7.1 Exercises

#1
When mutate is combined to grouping, the new column made is grouped and ordered by the variables given in the code.

#2
```{r}
arrange(flights, desc(tailnum))
```
#3
```{r}
arrange(flights, min_rank(dep_delay))
```
You should leave around 8pm.

#4
```{r}
flights %>%
  group_by(dest) %>%
  select(dest)
```

#5
```{r}
?lag
```


